### 2016-06-01 Chapters/intro.tex
Modifications on paper1 to unify the notation of the document

\section{Structure of the document}
Chapters \ref{chap-paper1}, \ref{chap-paper2} and \ref{chap-paper3} are based on the \comment{author's} articles \cite{badia_stabilized_2012}, \cite{badia_discrete_2015} and \cite{paper3} respectively. The three chapters follow the structure of the publications and, thus, are selfcontained.

>>>>

\section{Structure of the document}
Chapters \ref{chap-paper1}, \ref{chap-paper2} and \ref{chap-paper3} are based on the \comment{author's} articles \cite{badia_stabilized_2012}, \cite{badia_discrete_2015} and \cite{paper3} respectively. The three chapters follow the structure of the publications and, thus, are selfcontained. Some of the notation used might slightly differ from one chapter to another according to the necessities of each analysis. In this sense, on \ref{chap-paper3}, the elements of the mesh are ordered while in the rest they are not, and there is some abuse of notation on the solution space: it is called $\thn$ trough the document but it stnds for different concretizations in each of them (continuous or discontinuous).

\section{Things}
On the continuous Galerkin paradigm, the need of an extra linear stabilization seems to be obvious and the challenge faced in \ref{chap-paper1} will be how to blend the linear and nonlinear stabilization in such a way that one preserves the DMP property. The discontinuous Galerkin, on the other hand, do already have implicit linear stabilization in its definition so the artificial viscosity can be directly applied on the top of it.

### 2016-06-01 Chapters/paper1.tex
Modifications on paper1 to unify the notation of the document

In this work, we propose novel linear/nonlinear stabilized FE formulations to approximate hyperbolic problems (and by extension singular limits of CDR systems). The outcomes of this research are:
\begin{itemize}
\item  We extend the NPS technique proposed in \cite{badia_stabilized_2012} for pressure stabilization to convection stabilization. We carry out the stability and convergence analysis, getting full control on the convection term (times a stabilization parameter).\footnote{This is an improvement of our analysis with respect to the one in \cite{rebollo_high_2013} for a similar formulation, which only provides partial control over convection, i.e., the component orthogonal to the FE space with respect to the aforementioned projector. However, the analysis in \cite{rebollo_high_2013} is not restricted to quasi-uniform meshes.}
\item Next, we show how to weight this linear stabilization in such a way that it  does not affect the potential  monotonicity of the underlying method. The use of the Scott-Zhang projector in the NPS stabilization turns out to be essential to design a linear stabilization that allows one to preserve DMP properties. 
\item Then we present some nonlinear stabilization methods, i.e., shock-capturing schemes, with some  monotonicity properties. In particular, we design a method that enjoys a DMP for time-dependent multidimensional linear transport problems. 
%\item One of those methods is defined for the 1$D$ Burgers' equation and it is proved in  \cite{burman_nonlinear_2007} that it is not only monotonic but also entropy stable; thus an alternative blending between this nonlinear stabilization and the Scott-Zhang term is proposed in order to ensure that the combination mantains entropy stability.  
\item   We present a detailed numerical experimentation, where we show the excellent performance of the proposed algorithms in terms of elimination of oscillations, compared to some up-to-date shock-capturing schemes. 
%Using numerical experimentation, we show that one of the novel shock capturing techniques proposed in this work, %which can be considered a multidimensional extension of the one in \cite{burman_nonlinear_2007}, 
%produces results superior to any of the best up-to-date schemes, since it is provably monotonic. % (see \cite{john_spurious_2007,john_spurious_2008}). 
\end{itemize}

@@

Let us introduce some basic notation. Let  $q$ and $v$  be a scalar and vectorial smooth function respectively inside every element $K \in \mathcal{T}_h$. Let $K^+$ and $K^-$ be two neighboring elements and $\facet = \partial K^+ \cap \partial K^-$ the corresponding common face. We denote by $q^\pm$ (idem for $v^\pm$) the trace of $q$ on $\partial K^\pm$ taken within the interior of $K^\pm$, and $n^\pm$ the outward normal to $\partial K^\pm$. We define at $\x \in \facet$ the averages and jumps 
\begin{align*}
\mean{q} := \half(q^+ + q^-),\qquad \jump{q} &:=(q^+  n^+ + q^- n^-),\\
\mean{v} := \half(v^+ + v^-) ,\qquad \jump{v} &:= (v^+ \cdot n^+ + v^- \cdot n^-).
\end{align*}

%Further, we define $\jumpt{\v} := (\v^+ \otimes \n^+ + \v^- \otimes \n^-)$.
For the FE space $V_h^k$ we denote by $\mathcal{N}_h$ the set of all interpolation nodes related to $\mathcal{T}_h$ and by $\{\phi^a_h\}_{a \in \mathcal{N}_h}$ the corresponding nodal basis of $V_h^k$. We also denote by $\mathcal{N}_h(K)$ the set of all nodes that belong to a FE $K$. Continuous FE functions can be written as $v_h = \sum_{a \in \mathcal{N}_h} v_h^a \phi^a_h(\x)$, where $v_h^a$ denotes the nodal value of $v_h$ corresponding to $a$. Analogously, $\{\phi^a_h(\x)|_K\}_{K \in \mathcal{T}_h, a \in \mathcal{N}_h(K)}$ is the basis for $D_h$ and discontinuous FE functions  are written as $v_h = \sum_{K \in \mathcal{T}_h} \sum_{a \in \mathcal{N}_h(K)} v_h|_K^a \phi^a_h(\x)|_K$, where $v_h|_K^a$ is the value of $v_h$ at the node $a$ in element $K$.  
%Further, we define the adjacency list $\mathcal{A}_h^{\rm nd}(a)$ of a node $a \in \mathcal{N}_h$ as the set of nodes $c \in \mathcal{N}_h$ such that $a, c\in \mathcal{N}_h(K)$ for some $K \in \mathcal{T}_h$, i.e. the set of neighbor nodes. 
On the other hand, $\mathcal{A}_h^{\rm el}(a)$ is the set of elements $K \in \mathcal{T}_h$ such that $a \in \mathcal{N}_h(K)$, i.e., the set of neighbor elements, and $\Omega_a = \cup_{K\in\mathcal{A}_h^{\rm el}} K$ is the macroelement associated to the node $a$. Let  $h_K$ denote the diameter of $K\in\mathcal{T}_h$ and $h := \max_{K\in\mathcal{T}_h} h_K$.

@@

At this point, let us introduce a variant of the Scott-Zhang projector \cite{scott_finite_1990} which is well-defined for $L^1(\Omega)$ functions. The analysis in \cite{scott_finite_1990} does apply for this projector even though it is not the standard version, because it does not keep homogeneous boundary conditions. We can build a node-to-element map $\varsigma: \mathcal{N}_h \rightarrow  \mathcal{T}_h$ such that given a node $a$ it provides an element $K \in \mathcal{A}_h^{\rm el}(a)$; for interior nodes there is only one choice, two choices for nodes on faces and possibly more for nodes on edges or vertices. Following \cite{scott_finite_1990}, for any $a \in \mathcal{N}_h$ there is only one dual function $\psi^a_h \in P_r(K)$ (analogously for $Q_r(K)$) such that
\begin{align}\label{eq-dualfunct}
\int_{\varsigma(a)} \psi_h^a(\x)\phi_h^b(\x) {\rm d}\x = \delta_{ab}, \qquad \hbox{for any}\ b\in\mathcal{N}_h(\varsigma(a)).
\end{align}
Now, we construct the projector $\kappa_h: L^1(\Omega) \rightarrow V^k_h$ as follows:
\begin{align}\label{eq-projSZ}
\kappa_h(v) := \sum_{a \in \mathcal{N}_h}  \phi^a_h(\x) \int_{\varsigma(a)} \psi_h^a(\x) v(\x) \rm{d} \x.\end{align} 
However, we can consider the following simplifications:
\begin{enumerate}
\item Since $\nabla \phi^a_h|_K \in P_{r-1}(K) \subset P_r(K)$ for any $a \in \mathcal{N}_h$, we can easily check that $\kappa_h(\nabla \phi^a_h)(c) =  \nabla \phi^a_h|^c_ {\varsigma(c)}$ and thus, to compute the stabilization term \Eq{stproj1} one \emph{does not require any integration or the explicit computation of dual functions.} 
\item We note that this trick is not possible for \Eq{stproj2} since $\beta \cdot \nabla \phi^a_h|_K \not\in P_{r}(K)$ in general. However, we can still use the nodal projection, i.e., $\kappa_h(\beta \cdot \nabla \phi^a_h)(c) =  \beta \cdot \nabla \phi^a_h|^c_ {\varsigma(c)}$, keeping the required stability and approximability properties (see \cite{rebollo_high_2013}).
\end{enumerate}
We refer to \cite{badia_stabilized_2012} for a detailed discussion about implementation aspects and for the definition of the sparsity pattern of the matrix. 
%\begin{remark}
%Let us note that the previous projector does not keep any boundary condition, but it is not needed for our purposes. It allows us not to include the use of face (edge) integrals in the definition of the Scott-Zhang projector, making it well-posed for $L^1(\Omega)$ functions.
%\end{remark}

@@

\begin{definition} \label{strongDMP}
We say that the semi-linear form $a_h(u_h,\phi_h)$ has the strong DMP property if the following holds true: for any $u_h \in \vhk$ and for all interior vertex $a$, if $u_h$ is locally minimal (resp. maximal) on vertex $a$ over macroelement  $\Omega_a$ ($u_h(a)\leq u_h(x) \, \forall x\in \Omega_a$) then there exists $\alpha_K> 0$ such that
\begin{equation*}
a_h(u_h,\phi^a_h) \leq \sum_{K\in \Omega_a} \alpha_K |\nabla u_h |_K | \qquad \hbox{(resp. } a_h(u_h,\phi^a_h) \geq  \sum_{K\in \Omega_a} \alpha_K |\nabla u_h |_K | \hbox{)}.
\end{equation*}
%(resp. $a_h(u_h,\phi^a_h) \geq  \sum_{K\in \Omega_a} \alpha_K |\nabla u_h |_K |$).
\end{definition}
%It will be shown that if we use lumped matrices for the integration in time, the DMP implies that the method, if integrated exactly in time, has the total variation diminishing (TVD) property, meaning that neither maxima nor minima can appear in the solution for a zero force. 
It will be shown that, when using lumped matrices for the integration in time, the DMP implies that the local extrema are diminishing in time. The challenge is to find a linear stabilization that is capable to maintain this property. %As far as we know, the method proposed in this section is the first linear stabilization technique that does not spoil a DMP property when applied to the transient transport equation.\footnote{Let us remark that the work in \cite{burman_stabilized_2005} also combines linear and nonlinear stabilization, and a DMP property is proved. However, this work is restricted to the steady CDR problem and the extension to time-dependent problems is unclear, due to the fact that SUPG-type stabilization has been used.
%}
% nonlinear stabilization. We consider the artificial viscosity in \Eq{gjvisc}. This technique has been deeply analyzed in \cite{burman_nonlinear_2007} for the one-dimensional case. In the following subsections, we will show how to extend the setting in \cite{burman_nonlinear_2007} to include linear stabilization, and prove that our proposed blended formulation can keep all the desired properties of the nonlinear term, as soon as it is carefully chosen. Roughly speaking, the blending consists in switching off linear stabilization when nonlinear stabilization is active, i.e. around shocks and discontinuities. Further, the Scott-Zhang projector proves to be crucial to attain these properties.
%%We  want to solve the transport problem \Eq{probcont} and we assume that we already have a method, with associated bilinear form  $b_h(\cdot,\cdot)$, that satisfies the strong DMP property. In general, the bilinear form $b_h(\cdot,\cdot)$ will include the Galerkin terms and additional shock-capturing terms. Now, we add the NPS stabilization, $s_h(\cdot,\cdot)$, defined in \Eq{stproj1}-\Eq{projSZ}. Thus, the final system consists in finding $u_h\in \vh1$ such that
%% \begin{equation}
%% \label{eq-eq22}
%% (\partial_t u_h, \phi_h)_h + a_h(u_h;\phi_h) =0,  \qquad \forall \phi_h \in \vh1,
%% \end{equation}
%% where $a_h(u_h,\phi_h) = b_h(u_h,\phi_h) + s_h(u_h,\phi_h)$.

We want $a_h(\cdot,\cdot)$ to enjoy the strong DMP property and to do so we will  weight the value of $\delta$ in such a way that the term $s_h(\cdot,\cdot)$ does not harm the DMP property of $b_h(\cdot,\cdot)$. Let us introduce some definitions to compute this weighting. First let $a\in \mathcal{N}_h$ be a node of the mesh and $\mathbb{S}^d\subset \mathbb{R}^d$ be the unit sphere. We further introduce two new concepts: the jump on a node $a$, $\jump{v}_a$, and the mean value on a node $a$, $\mean{v}_a$. Given $v\in [D_h]^d$ be such that $v \cdot t$ is univalued on element boundaries, $t$ being an arbitrary tangent vector to the face (edge), we define these quantities as follows:
\begin{align}\label{eq-njump}
\jump{v}_a = \max_{\substack{ r\in\mathbb{S}^d }} \lim_{\varepsilon \rightarrow 0} (v(a+\varepsilon r)\cdot r - v(a-\varepsilon r)\cdot r),  
\quad \mean{v}_a = \frac{1}{2} \max_{\substack{ r\in\mathbb{S}^d }} \lim_{\varepsilon \rightarrow 0} (v(a+\varepsilon r)\cdot r + v(a-\varepsilon r)\cdot r).
\end{align}
Clearly, when $d=1$, these definitions reduce to the jump and the average of the absolute value on the corresponding node. The values are well defined for all $r$ %The argument in the limit is pointwise defined 
since the quantity $v \cdot r$ is univalued due to the tangential continuity of this function on element boundaries.

\begin{lemma}\label{lem-extrema}
 If $u_h\in\vh1$ has an extremum on node $a$, $ \frac{\jump{\nabla u_h}_a} { 2\mean{|\nabla u_h|}_a} = 1$. Further,  $ \frac{\jump{\nabla u_h}_a} { 2\mean{|\nabla u_h|}_a} \leq 1$ for any $a \in \mathcal{N}_h$.
\end{lemma}
\begin{proof}
Given $u_h \in V_h^1$, $\nabla u_h$ satisfies the tangential continuity on element boundaries above and the quantities in \Eq{njump} are well-defined. If $u_h$ has a local extremum on $a$, ${\rm sign} (\nabla u_h(a+r\varepsilon)) = -{\rm sign} (\nabla u_h(a-r\varepsilon))$ for any $ r\in \mathbb{S}^d$. Thus
\begin{align*}
\jump{\nabla u_h}_a = \jump{|\nabla u_h|}_a = & \max_{\substack{ r\in\mathbb{S}^d }} \lim_{\varepsilon \rightarrow 0} (|\nabla u_h(a+\varepsilon r)\cdot r - \nabla u_h(a-\varepsilon r)\cdot r|) \\
= &\max_{\substack{ r\in\mathbb{S}^d }} \lim_{\varepsilon \rightarrow 0} (|\nabla u_h(a+\varepsilon r)\cdot r | + |\nabla u_h(a-\varepsilon r)\cdot r|) =
2 \mean{|\nabla u_h|}_a.
\end{align*}
The upper bound is obvious. It proves the lemma.
\end{proof}

Finally, let us define the set $\mathcal{S}_h(K) = \{\varsigma(a) | a \in \mathcal{N}_h(K)\}$. Now we are able to define the  wNPS  weighting of $\delta$ in each element $K$ as:
\begin{align}\label{eq-tildeltaSZ}
\delta|_K = \frac{c_\delta h_K}{\|\beta\|_{L^\infty(K)}} \left(1-\max_{a \in \mathcal{S}_h(K)}\left(\frac{ \jump{\nabla u_h}_a }{2\mean{|\nabla u_h|}_a}\right)^q\right),
\end{align}
for $q>0$. The following theorem ensures the strong DMP property for $a_h(\cdot,\cdot)$.
\begin{theorem}
%Let the term $s_h(u_h,\phi_h)$ be defined as in \Eq{stproj1}-\Eq{projSZ}-\Eq{tildeltaSZ}. If $u_h$ has an extremum on $a$, then ${s}_h(u_h,\phi_h^a) = 0.$
Let $s_h(\cdot,\cdot)$ be  defined as \Eq{stproj1} or \Eq{stproj2}, with the projector $\kappa_h(\cdot)$ in \Eq{projSZ} and the stabilization parameter $\delta$ in \Eq{tildeltaSZ}. Then, if $b_h(\cdot,\cdot)$ enjoys the strong DMP property, so it does $a_h(\cdot,\cdot) =b_h(\cdot,\cdot) + s_h(\cdot,\cdot)$.
\end{theorem}
\begin{proof}First, we consider the expression \Eq{stproj1}. Let us check that if $u_h$ has an extremum on $a$, then ${s}_h(u_h,\phi_h^a) = 0.$ If $\kappa_h^\perp(\nabla \phi^a_h)|_K\neq 0$, there exists $b\in K$ such that $\varsigma (b) \in \mathcal{A}_h^{\rm el}(a)$. Thus $a\in  \mathcal{S}_h(K)$ and, since $u_h$ has an extremum on $a$,  $  \frac{ \jump{\nabla u_h }_a }{  2\mean{|\nabla u_h|}_a}=1$ and  $\delta|_K$ is $ 0$. Combining this result with Definition \ref{strongDMP} of the strong DMP property, we prove the theorem. The proof for the stabilization term \Eq{stproj1} is straighforward, observing that the same holds when $\kappa_h^\perp( \beta \cdot \nabla \phi^a_h)|_K\neq 0$.
\end{proof}

@@

\begin{lemma}
\label{lem-32}
Let the semilinear form $a_h(\cdot,\cdot)$ satisfy the strong DMP property. Then:
\begin{enumerate}
\item[i)]  If $u_h$ is the solution of $a_h(u_h;\phi_h) =f $ with $f\leq 0$ ( $f\geq 0$ resp.), then the minimum (the maximum resp.) of the solution is on the boundary of the domain $\Omega$.
\item[ii)] If  $u_h$ is the solution of \Eq{eq22}, any local extremum of $|u_h|$ is decreasing in time (LED). This implies that $ \| u_h \|_{L^\infty(0,T;L^\infty(\Omega))} \leq \| u_0 \|_{L^\infty(\Omega)}$. 
\end{enumerate}
\end{lemma}
\begin{proof}
\begin{enumerate}
\item[i)] If $u_h$ has a minimum on the node $a$ in the interior of $\Omega$ then $a_h(u_h,\phi_h^a)\leq \sum_{K\in \Omega_a} \alpha_K |\nabla u_h |_K |,$ for any $ \phi_h\in V_h^1$. But, since $f \leq 0$, we can deduce that $\nabla u_h |_K = 0$ for any $K\in \Omega_a$. Thus, $u_h(b)=u_h(a)$ for any node $b\in\Omega_a$. If $u_h(a)$ is maximal, so is $u_h(b)$ and the process can be repeated until one reaches a node $b\in \partial \Omega$. The proof for the maximum is analogous.

>>>>

In this chapter we introdue a linear/nonlinear stabilized FE formulations to approximate hyperbolic problems (and by extension singular limits of CDR systems). The outcomes of this research are:
\begin{itemize}
\item  We extend the NPS technique proposed in \cite{badia_stabilized_2012} for pressure stabilization to convection stabilization. We carry out the stability and convergence analysis, getting full control on the convection term (times a stabilization parameter).\footnote{This is an improvement of our analysis with respect to the one in \cite{rebollo_high_2013} for a similar formulation, which only provides partial control over convection, i.e., the component orthogonal to the FE space with respect to the aforementioned projector. However, the analysis in \cite{rebollo_high_2013} is not restricted to quasi-uniform meshes.}
\item Next, we show how to weight this linear stabilization in such a way that it  does not affect the potential  monotonicity of the underlying method. The use of the Scott-Zhang projector in the NPS stabilization turns out to be essential to design a linear stabilization that allows one to preserve DMP properties. 
\item Then we present some nonlinear stabilization methods, i.e., shock-capturing schemes, with some  monotonicity properties. In particular, we design a method that enjoys a DMP for time-dependent multidimensional linear transport problems. 
%\item One of those methods is defined for the 1$D$ Burgers' equation and it is proved in  \cite{burman_nonlinear_2007} that it is not only monotonic but also entropy stable; thus an alternative blending between this nonlinear stabilization and the Scott-Zhang term is proposed in order to ensure that the combination mantains entropy stability.  
\item   We present a detailed numerical experimentation, where we show the excellent performance of the proposed algorithms in terms of elimination of oscillations, compared to some up-to-date shock-capturing schemes. 
%Using numerical experimentation, we show that one of the novel shock capturing techniques proposed in this work, %which can be considered a multidimensional extension of the one in \cite{burman_nonlinear_2007}, 
%produces results superior to any of the best up-to-date schemes, since it is provably monotonic. % (see \cite{john_spurious_2007,john_spurious_2008}). 
\end{itemize}

@@

Let us introduce some basic notation. Let  $q$ and $v$  be a scalar and vectorial smooth function respectively inside every element $K \in \mathcal{T}_h$. Let $K^+_\facet$ and $K^-_\facet$ be two neighboring elements and $\facet = \partial K^+_\facet \cap \partial K^-_\facet$ the corresponding common face. We denote by $q^\pm$ (idem for $v^\pm$) the trace of $q$ on $\partial K^\pm_\facet$ taken within the interior of $K^\pm_\facet$, and $n^\pm$ the outward normal to $\partial K^\pm_\facet$. We define at $\x \in \facet$ the averages and jumps 
\begin{align*}
\mean{q} := \half(q^+ + q^-),\qquad \jump{q} &:=(q^+  n^+ + q^- n^-),\\
\mean{v} := \half(v^+ + v^-) ,\qquad \jump{v} &:= (v^+ \cdot n^+ + v^- \cdot n^-).
\end{align*}

%Further, we define $\jumpt{\v} := (\v^+ \otimes \n^+ + \v^- \otimes \n^-)$.
For the FE space $V_h^k$ we denote by $\setnodes$ the set of all interpolation nodes related to $\mathcal{T}_h$ and by $\{\varphi^i_h\}_{x_i \in \setnodes}$ the corresponding nodal basis of $V_h^k$. We also denote by $\setnodes(K)$ the set of all nodes that belong to a FE $K$. Continuous FE functions can be written as $v_h = \sum_{x_i \in \setnodes} v_h^i \varphi^i_h(\x)$, where $v_h^i$ denotes the nodal value of $v_h$ corresponding to $i$. Analogously, $\{\varphi^i_h(\x)|_K\}_{K \in \mathcal{T}_h, x_i \in \setnodes(K)}$ is the basis for $D_h$ and discontinuous FE functions  are written as $v_h = \sum_{K \in \mathcal{T}_h} \sum_{x_i \in \setnodes(K)} v_h|_K^i \varphi^i_h(\x)|_K$, where $v_h|_K^i$ is the value of $v_h$ at the node $x_i$ in element $K$.  
%Further, we define the adjacency list $\mathcal{A}_h^{\rm nd}(a)$ of a node $a \in \setnodes$ as the set of nodes $c \in \setnodes$ such that $a, c\in \setnodes(K)$ for some $K \in \mathcal{T}_h$, i.e. the set of neighbor nodes. 
On the other hand, $\Omega_i$ is the set of elements $K \in \mathcal{T}_h$ such that $x_i \in \setnodes(K)$, i.e., the set of neighbor elements. Let  $h_K$ denote the diameter of $K\in\mathcal{T}_h$ and $h := \max_{K\in\mathcal{T}_h} h_K$.

@@

At this point, let us introduce a variant of the Scott-Zhang projector \cite{scott_finite_1990} which is well-defined for $L^1(\Omega)$ functions. The analysis in \cite{scott_finite_1990} does apply for this projector even though it is not the standard version, because it does not keep homogeneous boundary conditions. We can build a node-to-element map $\varsigma: \setnodes \rightarrow  \mathcal{T}_h$ such that given a node $x_i$ it provides an element $K \in \Omega_i$; for interior nodes there is only one choice, two choices for nodes on faces and possibly more for nodes on edges or vertices. Following \cite{scott_finite_1990}, for any $x_i \in \setnodes$ there is only one dual function $\psi^i_h \in P_r(K)$ (analogously for $Q_r(K)$) such that
\begin{align}\label{eq-dualfunct}
\int_{\varsigma(x_i)} \psi_h^i(\x)\varphi_h^j(\x) {\rm d}\x = \delta_{ij}, \qquad \hbox{for any}\ j\in\setnodes(\varsigma(x_i)).
\end{align}
Now, we construct the projector $\kappa_h: L^1(\Omega) \rightarrow V^k_h$ as follows:
\begin{align}\label{eq-projSZ}
\kappa_h(v) := \sum_{x_i \in \setnodes}  \varphi^i_h(\x) \int_{\varsigma(x_i)} \psi_h^i(\x) v(\x) \rm{d} \x.\end{align} 
However, we can consider the following simplifications:
\begin{enumerate}
\item Since $\nabla \varphi^i_h|_K \in P_{r-1}(K) \subset P_r(K)$ for any $x_i \in \setnodes$, we can easily check that $\kappa_h(\nabla \varphi^i_h)(x_k) =  \nabla \varphi^i_h|^k_ {\varsigma(x_k)}$ and thus, to compute the stabilization term \Eq{stproj1} one \emph{does not require any integration or the explicit computation of dual functions.} 
\item We note that this trick is not possible for \Eq{stproj2} since $\beta \cdot \nabla \varphi^i_h|_K \not\in P_{r}(K)$ in general. However, we can still use the nodal projection, i.e., $\kappa_h(\beta \cdot \nabla \varphi^i_h)(x_k) =  \beta \cdot \nabla \varphi^i_h|^k_ {\varsigma(x_k)}$, keeping the required stability and approximability properties (see \cite{rebollo_high_2013}).
\end{enumerate}
We refer to \cite{badia_stabilized_2012} for a detailed discussion about implementation aspects and for the definition of the sparsity pattern of the matrix. 
%\begin{remark}
%Let us note that the previous projector does not keep any boundary condition, but it is not needed for our purposes. It allows us not to include the use of face (edge) integrals in the definition of the Scott-Zhang projector, making it well-posed for $L^1(\Omega)$ functions.
%\end{remark}

@@

\begin{definition} \label{strongDMP}
We say that the semi-linear form $a_h(u_h,\phi_h)$ has the strong DMP property if the following holds true: for any $u_h \in \vhk$ and for all interior vertex $x_i$, if $u_h$ is locally minimal (resp. maximal) on vertex $x_i$ over macroelement  $\Omega_i$ ($u_h(x_i)\leq u_h(x) \, \forall x\in \Omega_i$) then there exists $\alpha_K> 0$ such that
\begin{equation*}
a_h(u_h,\varphi^i_h) \leq \sum_{K\in \Omega_i} \alpha_K |\nabla u_h |_K | \qquad \hbox{(resp. } a_h(u_h,\varphi^i_h) \geq  \sum_{K\in \Omega_i} \alpha_K |\nabla u_h |_K | \hbox{)}.
\end{equation*}
%(resp. $a_h(u_h,\phi^a_h) \geq  \sum_{K\in \Omega_a} \alpha_K |\nabla u_h |_K |$).
\end{definition}
%It will be shown that if we use lumped matrices for the integration in time, the DMP implies that the method, if integrated exactly in time, has the total variation diminishing (TVD) property, meaning that neither maxima nor minima can appear in the solution for a zero force. 
It will be shown that, when using lumped matrices for the integration in time, the DMP implies that the local extrema are diminishing in time. The challenge is to find a linear stabilization that is capable to maintain this property. %As far as we know, the method proposed in this section is the first linear stabilization technique that does not spoil a DMP property when applied to the transient transport equation.\footnote{Let us remark that the work in \cite{burman_stabilized_2005} also combines linear and nonlinear stabilization, and a DMP property is proved. However, this work is restricted to the steady CDR problem and the extension to time-dependent problems is unclear, due to the fact that SUPG-type stabilization has been used.
%}
% nonlinear stabilization. We consider the artificial viscosity in \Eq{gjvisc}. This technique has been deeply analyzed in \cite{burman_nonlinear_2007} for the one-dimensional case. In the following subsections, we will show how to extend the setting in \cite{burman_nonlinear_2007} to include linear stabilization, and prove that our proposed blended formulation can keep all the desired properties of the nonlinear term, as soon as it is carefully chosen. Roughly speaking, the blending consists in switching off linear stabilization when nonlinear stabilization is active, i.e. around shocks and discontinuities. Further, the Scott-Zhang projector proves to be crucial to attain these properties.
%%We  want to solve the transport problem \Eq{probcont} and we assume that we already have a method, with associated bilinear form  $b_h(\cdot,\cdot)$, that satisfies the strong DMP property. In general, the bilinear form $b_h(\cdot,\cdot)$ will include the Galerkin terms and additional shock-capturing terms. Now, we add the NPS stabilization, $s_h(\cdot,\cdot)$, defined in \Eq{stproj1}-\Eq{projSZ}. Thus, the final system consists in finding $u_h\in \vh1$ such that
%% \begin{equation}
%% \label{eq-eq22}
%% (\partial_t u_h, \phi_h)_h + a_h(u_h;\phi_h) =0,  \qquad \forall \phi_h \in \vh1,
%% \end{equation}
%% where $a_h(u_h,\phi_h) = b_h(u_h,\phi_h) + s_h(u_h,\phi_h)$.

We want $a_h(\cdot,\cdot)$ to enjoy the strong DMP property and to do so we will  weight the value of $\delta$ in such a way that the term $s_h(\cdot,\cdot)$ does not harm the DMP property of $b_h(\cdot,\cdot)$. Let us introduce some definitions to compute this weighting. First let $x_i\in \setnodes$ be a node of the mesh and $\mathbb{S}^d\subset \mathbb{R}^d$ be the unit sphere. We further introduce two new concepts: the jump on a node $x_i$, $\jump{v}_i$, and the mean value on a node $x_i$, $\mean{v}_i$. Given $v\in [D_h]^d$ be such that $v \cdot t$ is univalued on element boundaries, $t$ being an arbitrary tangent vector to the face (edge), we define these quantities as follows:
\begin{align}\label{eq-njump}
\jump{v}_i = \max_{\substack{ r\in\mathbb{S}^d }} \lim_{\varepsilon \rightarrow 0} (v(x_i+\varepsilon r)\cdot r - v(x_i-\varepsilon r)\cdot r),\\  
\quad \mean{v}_i = \frac{1}{2} \max_{\substack{ r\in\mathbb{S}^d }} \lim_{\varepsilon \rightarrow 0} (v(x_i+\varepsilon r)\cdot r + v(x_i-\varepsilon r)\cdot r).
\end{align}
Clearly, when $d=1$, these definitions reduce to the jump and the average of the absolute value on the corresponding node. The values are well defined for all $r$ %The argument in the limit is pointwise defined 
since the quantity $v \cdot r$ is univalued due to the tangential continuity of this function on element boundaries.

\begin{lemma}\label{lem-extrema}
 If $u_h\in\vh^1$ has an extremum on node $x_i$, $ \frac{\jump{\nabla u_h}_i} { 2\mean{|\nabla u_h|}_i} = 1$. Further,  $ \frac{\jump{\nabla u_h}_i} { 2\mean{|\nabla u_h|}_i} \leq 1$ for any $x_i \in \setnodes$.
\end{lemma}
\begin{proof}
Given $u_h \in V_h^1$, $\nabla u_h$ satisfies the tangential continuity on element boundaries above and the quantities in \Eq{njump} are well-defined. If $u_h$ has a local extremum on $x_i$, ${\rm sign} (\nabla u_h(x_i+r\varepsilon)) = -{\rm sign} (\nabla u_h(x_i-r\varepsilon))$ for any $ r\in \mathbb{S}^d$. Thus
\begin{align*}
\jump{\nabla u_h}_i = \jump{|\nabla u_h|}_i = & \max_{\substack{ r\in\mathbb{S}^d }} \lim_{\varepsilon \rightarrow 0} (|\nabla u_h(x_i+\varepsilon r)\cdot r - \nabla u_h(x_i-\varepsilon r)\cdot r|) \\
= &\max_{\substack{ r\in\mathbb{S}^d }} \lim_{\varepsilon \rightarrow 0} (|\nabla u_h(x_i+\varepsilon r)\cdot r | + |\nabla u_h(x_i-\varepsilon r)\cdot r|) =
2 \mean{|\nabla u_h|}_i.
\end{align*}
The upper bound is obvious. It proves the lemma.
\end{proof}

Finally, let us define the set $\mathcal{S}_h(K) = \{\varsigma(x_i) | x_i \in \setnodes(K)\}$. Now we are able to define the  wNPS  weighting of $\delta$ in each element $K$ as:
\begin{align}\label{eq-tildeltaSZ}
\delta|_K = \frac{c_\delta h_K}{\|\beta\|_{L^\infty(K)}} \left(1-\max_{x_i \in \mathcal{S}_h(K)}\left(\frac{ \jump{\nabla u_h}_i }{2\mean{|\nabla u_h|}_i}\right)^q\right),
\end{align}
for $q>0$. The following theorem ensures the strong DMP property for $a_h(\cdot,\cdot)$.
\begin{theorem}
%Let the term $s_h(u_h,\varphi_h)$ be defined as in \Eq{stproj1}-\Eq{projSZ}-\Eq{tildeltaSZ}. If $u_h$ has an extremum on $a$, then ${s}_h(u_h,\varphi_h^a) = 0.$
Let $s_h(\cdot,\cdot)$ be  defined as \Eq{stproj1} or \Eq{stproj2}, with the projector $\kappa_h(\cdot)$ in \Eq{projSZ} and the stabilization parameter $\delta$ in \Eq{tildeltaSZ}. Then, if $b_h(\cdot,\cdot)$ enjoys the strong DMP property, so it does $a_h(\cdot,\cdot) =b_h(\cdot,\cdot) + s_h(\cdot,\cdot)$.
\end{theorem}
\begin{proof}First, we consider the expression \Eq{stproj1}. Let us check that if $u_h$ has an extremum on $x_i$, then ${s}_h(u_h,\varphi_h^i) = 0.$ If $\kappa_h^\perp(\nabla \varphi^i_h)|_K\neq 0$, there exists $x_j\in K$ such that $\varsigma (j) \in \Omega_i$. Thus $x_i\in  \mathcal{S}_h(K)$ and, since $u_h$ has an extremum on $x_i$,  $  \frac{ \jump{\nabla u_h }_i }{  2\mean{|\nabla u_h|}_i}=1$ and  $\delta|_K$ is $ 0$. Combining this result with Definition \ref{strongDMP} of the strong DMP property, we prove the theorem. The proof for the stabilization term \Eq{stproj1} is straighforward, observing that the same holds when $\kappa_h^\perp( \beta \cdot \nabla \varphi^i_h)|_K\neq 0$.
\end{proof}

@@

\begin{lemma}
\label{lem-32}
Let the semilinear form $a_h(\cdot,\cdot)$ satisfy the strong DMP property. Then:
\begin{enumerate}
\item[i)]  If $u_h$ is such that $a_h(u_h;\phi_h) =f $  for any $ \phi_h\in V_h^1$ with $f\leq 0$ ( $f\geq 0$ resp.), then the minimum (the maximum resp.) of the solution is on the boundary of the domain $\Omega$.
\item[ii)] If  $u_h$ is the solution of \Eq{eq22}, any local extremum of $|u_h|$ is decreasing in time (LED). This implies that $ \| u_h \|_{L^\infty(0,T;L^\infty(\Omega))} \leq \| u_0 \|_{L^\infty(\Omega)}$. 
\end{enumerate}
\end{lemma}
\begin{proof}
\begin{enumerate}
\item[i)] If $u_h$ has a minimum on the node $x_i$ in the interior of $\Omega$ then $a_h(u_h,\varphi_h^i)\leq \sum_{K\in \Omega_i} \alpha_K |\nabla u_h |_K |,$. But, since $f \leq 0$, we can deduce that $\nabla u_h |_K = 0$ for any $K\in \Omega_i$. Thus, $u_h(x_j)=u_h(x_i)$ for any node $x_j\in\Omega_i$. If $u_h(x_i)$ is maximal, so is $u_h(x_j)$ and the process can be repeated until one reaches a node $x_j\in \partial \Omega$. The proof for the maximum is analogous.
